Reconstruction of Large Scale Structure by Nonlinear Displacement Fields

### 2016-09-21 ms_disp1/ms_disp1.tex
disp paper figures preliminary

In this paper we track the initial and final distributions of particles in LSS $N$-body simulations, and use the displacement field to reconstruct the initial linear density field. The rest of this paper is structured as follows. In section \ref{sec.method} we describe the simulation and reconstruction algorithm. In section \ref{sec.results} we show the results of the reconstruction. Discussion and conclusion are in \ref{sec.discussion}.

@@

\subsection{Reconstruction}
In the simulation, we uses particle-ID (PID) to record the initial location ${\bs q}$ of particles, and the information is tracked until the $z=0$ and we can get the Lagrangian displacement vector ${\bs \Psi}\equiv{\bs x}-{\bs q}$ for every particle. Then these vectors are interpolated onto the initial Lagrangian coordinates ${\bs q}$ of particles and we get the displacement field ${\bs \Psi}({\bs q})$.
The raw reconstructed density field is given by the differential motion of matter elements,
\begin{equation}
    \delta_R=-\nabla\cdot{\bs \Psi}({\bs q}).
\end{equation}

To quantify the linear information in the reconstructed density field, we decompose $\delta_R$ in Fourier space as
\begin{equation}\label{eq.decompose}
    \delta_R(k)=r'\delta_L+\delta_N,
\end{equation}
where $r'\delta_R$ is completely correlated with linear density $\delta_L$. Correlating equation (\ref{eq.decompose}) with $\delta_L$ gives
\begin{equation}
    P_{LR}=r'P_{LL}+P_{LN}
\end{equation}
where $P_{ij}\equiv\lb\delta_i\delta_j\rb$ denotes the cross power spectrum. Since $\delta_N$ is uncorrelated with $\delta_L$, $P_{LN}=0$. With the definition of cross correlation coefficient $r\equiv P_{LR}/\sqrt{P_{LL}P_{RR}}$ and bias $b^2=P_{RR}/P_{LL}$, we solve $r'=P_{LR}/P_{LL}=rb$. According to equation (\ref{eq.decompose}), the auto power spectrum is decomposed as
\begin{equation}
    P_{RR}=r^2b^2P_{LL}+P_{NN},
\end{equation}
and $P_{NN}=(1-r^2)P_{RR}$. Then we construct a Wiener filter to filter out the uncorrelated part in $\delta_R$:
\begin{equation}
    W(k)=\frac{r^2b^2P_{LL}}{r^2b^2P_{LL}+P_{NN}}=r^2.
\end{equation}
The estimated linear density, or the optimal reconstructed density is given by
\begin{equation}
    \tilde\delta_R=Wb^{-1}\delta_R,
\end{equation}
and the optimal reconstructed power spectrum is given by
\begin{equation}
    \tilde P=W^2b^{-2}P_{RR}=W^2P_{LL}+W^2b^{-2}P_{NN}.
\end{equation}

%\begin{figure}[t] \centering
%  \includegraphics[width=1.0\linewidth]{fig1.pdf}
%  \caption{Caption goes here.}
%  \label{fig.1}
%\end{figure}

\section{Results}\label{sec.results}

>>>>

In this paper we track the initial and final distributions of particles in LSS $N$-body simulations, and use the displacement field to reconstruct the initial linear density field. The rest of this paper is structured as follows. In section \ref{sec.method} we describe the simulation and reconstruction algorithm. In section \ref{sec.results} we show the results of the reconstruction. Discussion and conclusion are in section \ref{sec.discussion}.

\begin{figure}[b] \centering
  \includegraphics[width=1.0\linewidth]{fig1.pdf}
  \caption{Dimensionless auto- and cross- power spectra between nonlinear density field $\delta$, linear density field $\delta_L$ and reconstructed density field $\delta_R$.}
  \label{fig.1}
\end{figure}
\begin{figure}[t] \centering
  \includegraphics[width=1.0\linewidth]{fig2.pdf}
  \caption{Caption goes here.}
  \label{fig.2}
\end{figure}

@@

Two-point statistics of the density fields are quantified by the cross power spectrum $P_{ij}(k)\equiv(2\pi)^{-3}\langle|\delta_i(k)\delta_j(k)|\rangle$, where subscripts $i,j$ may refer to linear, nonlinear, or reconstructed density fields. When $i=j$ it reduces to the auto power spectrum $P_{ii}(k)$ or $P(k)$. We usually plot the dimensionless power spectrum $\Delta^2(k)\equiv k^3P(k)/2\pi^2$. The blue solid and black dashed curves in Fig.\ref{fig.1} show the power spectra of $\delta$ and $\delta_L$. Their difference shows the nonlinear evolution of LSS on small scales. Their cross power drops to a very low value, indicating a loss of linear information in the nonlinear power spectrum.

\subsection{Reconstruction}
In the simulation, we uses particle-ID (PID) to record the initial location ${\bs q}$ of particles, and the information is tracked until the $z=0$ and we can get the Lagrangian displacement vector ${\bs \Psi}\equiv{\bs x}-{\bs q}$ for every particle. Then these vectors are interpolated onto the initial Lagrangian coordinates ${\bs q}$ of particles and we get the displacement field ${\bs \Psi}({\bs q})$.
The raw reconstructed density field is given by the differential motion of matter elements,
\begin{equation}
    \delta_R=-\nabla\cdot{\bs \Psi}({\bs q}).
\end{equation}
In Fig.\ref{fig.1} we show the power spectrum of $\delta_R$ and its cross power with $\delta_L$. Despite of a lowered power of $\delta_R$ compared to $\delta$, it has a much higher cross power with $\delta_L$, up to a relatively smaller scale (higher $k$).

To quantify the linear information in the reconstructed density field, we decompose $\delta_R$ in Fourier space as
\begin{equation}\label{eq.decompose}
    \delta_R(k)=r'\delta_L+\delta_N,
\end{equation}
where $r'\delta_R$ is completely correlated with linear density $\delta_L$. Correlating equation (\ref{eq.decompose}) with $\delta_L$ gives
\begin{equation}
    P_{LR}=r'P_{LL}+P_{LN},
\end{equation}
where $P_{ij}\equiv\langle\delta_i\delta_j\rangle$ denotes the cross power spectrum. Since $\delta_N$ is uncorrelated with $\delta_L$, $P_{LN}=0$. With the definition of cross correlation coefficient $r\equiv P_{LR}/\sqrt{P_{LL}P_{RR}}$ and bias $b^2=P_{RR}/P_{LL}$, we solve $r'=P_{LR}/P_{LL}=rb$. We plot the cross correlation coefficient $r_{LN}$ and $r_{LR}$ in Fig.\ref{fig.2}. Clearly, $\delta_R$ contains much more linear information on smaller scales.

According to equation (\ref{eq.decompose}), the auto power spectrum is decomposed as
\begin{equation}
    P_{RR}=r^2b^2P_{LL}+P_{NN},
\end{equation}
and $P_{NN}=(1-r^2)P_{RR}$. Then we construct a Wiener filter to filter out the uncorrelated part in $\delta_R$:
\begin{equation}
    W(k)=\frac{r^2b^2P_{LL}}{r^2b^2P_{LL}+P_{NN}}=r^2.
\end{equation}
The Wiener filters are also plot in Fig.\ref{fig.2}. The estimated linear density, or the optimal reconstructed density is given by
\begin{equation}
    \tilde\delta_R=Wb^{-1}\delta_R.
\end{equation}
The full filters $Wb^{-1}$ are also plotted in Fig.\ref{fig.2}. The optimal reconstructed power spectrum is given by
\begin{equation}
    \tilde P=W^2b^{-2}P_{RR}=W^2P_{LL}+W^2b^{-2}P_{NN}.
\end{equation}
The $W^2$ describes the damping of the linear power spectrum.

\begin{figure}[t] \centering
  \includegraphics[width=1.0\linewidth]{fig3.pdf}
  \caption{Caption goes here.}
  \label{fig.3}
\end{figure}

\begin{figure}[t] \centering
  \includegraphics[width=1.0\linewidth]{fig4.pdf}
  \caption{Caption goes here.}
  \label{fig.4}
\end{figure}

\section{Results}\label{sec.results}
Fig.\ref{fig.2} shows the damping factors $W^2(k)$ for the optimal filtered nonlinear and reconstructed density fields. We fit the Gaussian BAO damping model ${\mathcal D}(k)=\exp(-k^2\Sigma^2/2)$ and give $\Sigma=1.8$ Mpc$/h$ and $\Sigma=10$ Mpc$/h$ for nonlinear and reconstructed fields.
